### 2018-03-06 Paper/jaccardbaetica.tex
change methods and results

The analysis explores how quantitative approach provides a useful tool for the interpretation of the economic processes. Finally, results pretend to highlight the organization of olive oil production in the Roman Empire linked to the differences observed in the archaeological evidence.

@@

@@

However, the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 990 stamps composed by 131 different stamps from 81 workshops.

@@

The approach proposed here is based on the idea of measuring the similarity between amphora workshops by quantifying similar stamps. A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index. This method was performed to measure the overlap between different samples of sets \citep{morisita_measuring_1959, horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

@@

>>>>

The analysis explores how quantitative approach provides a useful tool for the interpretation of the economic processes. Finally, results pretend to highlight the organization of Baetican olive oil production in the Roman Empire linked to the differences observed in the archaeological evidence.

@@

Here, therefore, this study aim to explore the effect of Baetican olive oil production in the Roman Empire
of production organization over Baetican olive oil production.

@@

However, the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps composed by 131 different stamps from 81 workshops.

@@

The approach proposed here is based on the idea of measuring the similarity between amphora workshops by quantifying similar stamps. A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index. The formula can be described as follows

(FORMULA Y DESCRIPCIÓN)

This method was performed to measure the overlap between different samples of sets \citep{morisita_measuring_1959, horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

@@

Some closest workshops show a similarity on the stamps such as BLA BLA BLA . This could be due to several reasons.

doesn't support

As summary, these results
